Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-16 paper.tex
Fix typo and add the word 'slight'

Full power and rotor drag (a.k.a. thrust) coefficient curves for various
Reynolds numbers are plotted in Figure~\ref{fig:cp-curves} and
Figure~\ref{fig:cd-curves}, respectively. In general, maximum $C_P$ increases
with Reynolds number. The power coefficient curves also show a slight downward
shift in the optimal tip speed ratio (peak performance) with increasing Reynolds
number, from about $\lambda \approx$ 2.0 to 1.9. This is caused by the stall
delay from a more turbulent boundary later on the blade suction side. There is
essentially no change in the shape of the drag coefficient curves---merely an
upward shift in $C_D$ with increasing $Re$.

>>>>

Full power and rotor drag (a.k.a. thrust) coefficient curves for various
Reynolds numbers are plotted in Figure~\ref{fig:cp-curves} and
Figure~\ref{fig:cd-curves}, respectively. In general, maximum $C_P$ increases
with Reynolds number. The power coefficient curves also show a slight downward
shift in the optimal tip speed ratio (peak performance) with increasing Reynolds
number, from about $\lambda \approx$ 2.0 to 1.9. This is caused by the stall
delay from a more turbulent boundary layer on the blade suction side. There is
essentially no change in the shape of the drag coefficient curves---merely a
slight upward shift in $C_D$ with increasing $Re$.
